### 2020-06-17 myThesis/thesis_LaTeX/main.tex
thesis structure
title typo
thesis characterization chapter added
thesis - alpha_rate_fitting - new articles

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Fabrication of graphitic-carbon suspended nanowires through mechanoelectrospinning of photocrosslinkable polymers}

@@

I offer my gratitude and appreciation to my supervisors, \supname and \cosupname, for the deft ways in which you lovingly challenged and supported me through out the whole of this work - knowing when to push and when to let up. I offer special thanks to those who supported me in the mechanics of producing this thesis. \supname, for reading and rereading drafts, editing and proofing, typing and helping me get ‘unstuck’ with this thesis on many occasions. And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.

@@

\include{./Chapters/1}
\include{./Chapters/2}
\include{./Chapters/3}
\include{./Chapters/4}
\include{./Chapters/5}
\include{./Chapters/6}
\include{./Chapters/7}

>>>>

% Your thesis title, this is used in the title and abstract, print it elsewhere with \ttitle
\thesistitle{Fabrication of Graphitic-Carbon Suspended Nanowires Through Mechano-Near-Field Electrospinning of Photocrosslinkable Polymers}

@@

I offer my gratitude and appreciation to my supervisors, \supname and \cosupname, for the deft ways in which you fondly challenged and supported me through out the whole of this work - knowing when to push and when to let up. I offer special thanks to those who supported me in the mechanics of producing this thesis. \supname, for reading and rereading drafts, editing and proofing, typing and helping me get ‘unstuck’ with this thesis on many occasions. And Braulio and Arnoldo for ‘rescuing’ me at those times when I was almost defeated by the laboratory equipment.

@@

\include{./Chapters/1}
\include{./Chapters/2}
\include{./Chapters/3}
\include{./Chapters/4}
\include{./Chapters/5}
\include{./Chapters/6}
%\include{./Chapters/7}
